---
title: "ENVST193DS_HW3"
output: html_document
---

https://github.com/misssammwoods04/ENVS_193DS_homework-03.git

```{r}

library(tidyverse)
library(here)
library(flextable)
library(janitor)
library(readxl)

p_data <- read.csv("PersonalData.csv")

```


# Problem 1

## a.         

For each number of assignments I have (0-5), I can find the rate at which I leave campus based on how many times I have left campus for a certain number of assignments. This comparison would be informative because I believe that my stress level increases with the number of assignments I have, and I believe that I would be more likely to leave campus on the days that my stress is high. 

## b.
```{r}
 clean_p_data <- p_data |> 
  clean_names()
```


```{r}

ggplot(clean_p_data, aes(x = x_hw_to_do, y = leave_iv_campus_home)) +
  geom_jitter(height = 0.05, 
              width = 0.2, 
              alpha = 0.4, 
              color = "purple",
              size = 7,
              pch = 1,
              stroke = 1.5) +
  labs(
    title = " Leaving School vs. Assignments",
    x = "Number of Assignments",
    y = "Did I Leave School? (1 = Yes, 0 = No)"
  ) +
  theme_minimal()
          
```



